The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-07-25 ApJ/ms.tex
Some more additions and changes to added content.

\begin{figure}
\epsscale{1.15}
\plotone{f1}
\epsscale{1}
\caption{\label{fig:massfn} \textit{Top}: Halo mass function of the
  simulation compared with the analytical fit (solid) of
  \citet{Warren06}.  \textit{Bottom}: Total Pop II luminosities of
  halos versus dark matter halo mass with constant mass-to-light
  ratios overplotted.}
\end{figure}

@@

Here we first present the global star formation rate (SFR) and metal
enrichment during early galaxy formation and then focus on the gaseous
and stellar evolution of two selected halos in the simulation: one
that has an early mass buildup but no major mergers after $z=12$, and
one that experiences a series of major mergers between $z=10$ and
$z=7$.  We name the halos ``quiet'' and ``intense'', respectively.
The entire simulation contains 38 galaxies with 3640 Pop II stellar
clusters and captures the formation of 333 Pop III stars.  The halo
mass function and galaxy luminosities are plotted in Figure
\ref{fig:massfn}.

@@

\subsection{Pre-enrichment from Population III stars}

@@

@@

@@

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \citep{Wolfe05_Review}, and metal enrichment from Pop
III SNe provides a possible explanation.

>>>>

@@

Here we first present the global star formation rate (SFR) during
early galaxy formation and then focus on the gaseous and stellar
evolution of two selected halos in the simulation: one that has an
early mass buildup but no major mergers after $z=12$, and one that
experiences a series of major mergers between $z=10$ and $z=7$.  We
name the halos ``quiet'' and ``intense'', respectively.  The entire
simulation contains 38 galaxies with 3640 Pop II stellar clusters and
captures the formation of 333 Pop III stars.

@@

@@

To further demonstrate the metallicity floor in high-redshift dwarf
galaxies, we show the average metallicity from Pop III SNe \zthree~in
all haloes as a function of halo mass at $z =$ 7, 8, 9, and 10 in
Fig. \ref{fig:z3}, and it is strongly dependent on halo mass.  The
\zthree~error bars mark the 25\% and 75\% percentiles of the
distribution at $M = M_{\rm halo}$ because the underlying distribution
is not necessarily Gaussian at all halo masses.  Above $3 \times 10^7
\Ms$, all haloes enriched to $\zthree \ga -4$ with little time
evolution, further illustrating the metallicity floor.  Below this
halo mass, the distribution is roughly bimodal composed of pristine
and metal-enriched halos.

@@

\subsection{Mass-to-light ratios}

\begin{figure}
\epsscale{1.15}
\plotone{f1}
\epsscale{1}
\caption{\label{fig:massfn} Total Pop II luminosities of halos versus
  total halo mass with constant mass-to-light ratios overplotted.}
\end{figure}

Mass-to-light ratios are crucial in interpreting observations when
connecting the galaxy to its DM halo, and ultimately to models of
galaxy formation.  For this paper, we use a simple model to calculate
the total stellar luminosity of each galaxy.  In a later paper, we
will follow up with more sophisicated models to determine more
accurate observables.  Stars in each particle are treated an
instantaneous burst.  Using the empirical law of main sequence
lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
such a system is dependent only on its age $t_\star$, so $M_{\rm up} =
(t_\star / 10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling
law $L \propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto
M^{-\alpha}$,
%
\begin{eqnarray}
  \label{eqn:lum}
  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM
  \nonumber\\ &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
\end{eqnarray}
where we set $M_{\rm lo} \equiv 0$ because it is negligible in the
luminosity.  Then the galaxy luminosity is the sum of all star
particle luminosities, which we plot in Fig. \ref{fig:massfn} with
respect to halo mass, along with the DM halo mass function.

Recall that the most massive halo ($M_{\rm tot} = 10^9 \Ms$) is
undergoing a starburst at $z=7$, translating into a relatively high
$M/L = 6$.  The lower mass galaxies show a spread in M/L over two
orders of magnitude, similar to the Sloan Digital Sky Survey (SDSS)
observations of local dSph galaxies \citep[e.g.][]{Strigari08}.

@@

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \citep{Wolfe05_Review}, and metal enrichment from Pop
III SNe provides a possible explanation \citep{Kobayashi11}.
